---
title: "index"
author: "Yujia Si"
date: "11/12/2020"
output: html_document
---

```{r setup, include=FALSE}
library("knitr")
knitr::opts_knit$set(root.dir = './scripts')
```

## Introduction
As not only individuals who are experiencing this unprecedented time of a global pandemic and emergency, but as students at the University of Washington, where fellow peers and others have unfortunately been not so pandemic-friendly in their practices, causing outbreaks to surge, Covid-19 and the current response has been all-consuming in our lives through its impact on our sense of normalcy and safety as it has for people of any race. As we continue to see numbers rise and tensions grow, this issue and the overall instance have grown to be a great topic of interest for our group. It has deeply affected our families and us individually, and we are eager to learn and discover more by delving deep into the subject. We are interested in finding out how Covid-19 has impacted people of different race in the United States based on two of the datasets we've found(https://github.com/info201b-au20/project-covid/blob/gh-pages/data/PUBLIC_CDC_Event_Date_SARS.xlsx, https://github.com/info201b-au20/project-covid/blob/gh-pages/data/Race%20Data%20Entry%20-%20CRDT.csv).
## Summary
```{r, include=FALSE}
source("./scripts/summary.R")
```
In the summary section, we wanted to explore the number of people of different races who were tested positive for Covid-19. First off, we figured out the number of features and obervations of the dataset. Then we 
## Table
```{r}
weekly_county_age_cases
```
This table summarizes the number of weekly new cases by 
```{r}
cumulative_cases_by_race
```
This table summarizes the number of weekly new cases by 
```{r}
rate_cases_by_race
```
This table summarizes the number of weekly new cases by 

## Visualization
#### Chart 1: Cumulative Amount of Total Reported COVID-19 Cases in the State of Washington by Racial Groups
```{r}
source("./scripts/BarChart.R")
```
The purpose of this chart is to show the cumulative amount of total reported COVID-19 cases in the state of Washington by racial groups. Due to the nature of the chart being cumulative, a bar chart accurately captures the total value (cases) of the different categories (racial groups). What is notable about this chart is the overwhelming amount of race “Unknown” cases there are as that impacts the data and alters the information drawn from the set as well. It is also important to note the large amount of cases recorded as “White” and “Hispanic/Latino” in comparison to the other groups considered. These two observations are especially insightful in terms of the disparities seen in recording cases by race, which lead to a more narrowed and misleading perception as to how the pandemic is effecting certain communities. For example, the Black community as well as the American Indian community, which has notably been heavily impacted and harmed by COVID-19, but the data seems to paint a different tale. On the other hand, the number surrounding Hispanic/Latino populations seem to align with what we know in terms of how heavily migrant workers in more rural, agricultural parts of Washington have been ravaged by the virus.

#### Chart 2: How Different Age Groups Are Affected By Covid-19
```{r}
source("./scripts/ViolinPlot.R")
```
The purpose of including this chart is to see how different age groups are
affected by Covid-19, and to see which groups contribute most the number of
cases present. In this plot we are able to that the most mean number of weekly
cases is from the age 20-39 group, this group is also has the max number of 
cases in a pparticular week during the time of data collection

#### Chart 3:
```{r}
source("./scripts/")
```




